---
title: "GitHub, OneDrive, and Records! Oh My!"
author: "Jeffrey W. Hollister"
date: '`r Sys.Date()`'
output:
  html_document:
    theme: readable
    toc: yes
    toc_float: yes
vignette: >
  %\VignetteIndexEntry{GitHub, OneDrive, and Records! Oh My!} 
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown} 
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE, echo=FALSE}
################################################################################
#Load packages
################################################################################
library("epar")
NOT_CRAN <- identical(tolower(Sys.getenv("NOT_CRAN")), "true")
knitr::opts_chunk$set(purl = NOT_CRAN, 
                      eval = NOT_CRAN,
                      fig.width = 4, 
                      fig.height = 4, 
                      tidy = TRUE,
                      dpi = 100)
```

```{r environ, echo=FALSE}
#key <- readRDS("../tests/testthat/key_file.rds")
#Sys.setenv(mapzen_key=key)
```

# TL;DR

If you have a GitHub and local git repository that is not on OneDrive (e.g. git repos and OneDrive are best to not be mixed!), we can set up a mirror on OneDrive that will satisfy records requirements because EPA does not consider GitHub repos as records.  Our files on OneDrive are records and are backed up.  

If you are working in R in the git repository (aside: An RStudio project would be an excellent way to manage this) you can do the following to set up a mirror repo on OneDrive.

First, make sure you have the `epar` pacakge installed from GitHub.

```{r eval=FALSE}
remotes::install_github("usepa/epar")
library(epar)
```

With that taken care of we can use the `add_mirror_repo()` and `one_drive_mirror()` functions to get everything set up.

```{r eval=FALSE}
mirror <- one_drive_mirror("projects")
add_mirror_repo(mirror)
```

For details read the rest!

# Records and GitHub Repos

Stuff

# Options for Records

Stuff

# Git and OneDrive

Stuff

# Git Workflow

Stuff

# Solution

Stuff
